---
title: "more_infos_about_test"
date : "October 29, 2017"
output: html_document
---

```{r}
sum( ! (test$msno) %in% train$msno) / length(test$msno)
```

7.19% (184,018 lines) msno of test are not in train. 
==> That quantity of prediction must be made without knowing a particular user's taste


```{r}
sum( ! (unique(test$msno) %in% unique(train$msno))) / length(unique(test$msno))
```
in terms of unique users, 14.5% of unique msno in test are not in train...

(of course, each msno in members is unique)
```{r}
sum(unique(test$msno) %in% members$msno) / length(unique(test$msno))
```
...Yet, all test data subjects are referenced in members


What infos do we know about these users just from members dataset ?

=>checks quality of attributes globally. If equals 0, then all infos are complete
subsets to members users from test which are not in train
```{r}
users_unknown_tastes <- train[which(! (unique(test$msno) %in% unique(train$msno))) , ]$msno
users_unknown_tastes <- members[(members$msno %in% users_unknown_tastes), ]
```
---------for city---------
```{r}
sum(sapply(X = users_unknown_tastes$city, FUN = is.na)) / length(users_unknown_tastes$city)
sum(sapply(X = users_unknown_tastes$city, FUN = is.null)) / length(users_unknown_tastes$city)
```
---------for bd---------
```{r}
sum(sapply(X = users_unknown_tastes$bd, FUN = is.na)) / length(users_unknown_tastes$bd)
sum(sapply(X = users_unknown_tastes$bd, FUN = is.null)) / length(users_unknown_tastes$bd)
```
Still must check what is the proportion of "reliable" ages (not extremes)
---------for registered_via---------
```{r}
sum(sapply(X = users_unknown_tastes$registered_via, FUN = is.na)) / length(users_unknown_tastes$registered_via)
sum(sapply(X = users_unknown_tastes$registered_via, FUN = is.null)) / length(users_unknown_tastes$registered_via)
```
---------for registration_init_time---------
```{r}
sum(sapply(X = users_unknown_tastes$registration_init_time, FUN = is.na)) / length(users_unknown_tastes$registration_init_time)
sum(sapply(X = users_unknown_tastes$registration_init_time, FUN = is.null)) / length(users_unknown_tastes$registration_init_time)
```
---------for expiration_date---------
```{r}
sum(sapply(X = users_unknown_tastes$expiration_date, FUN = is.na)) / length(users_unknown_tastes$expiration_date)
sum(sapply(X = users_unknown_tastes$expiration_date, FUN = is.null)) / length(users_unknown_tastes$expiration_date)
```
---------for gender---------
```{r}
sum(users_unknown_tastes$gender == "") / length(users_unknown_tastes$gender)
```
39% of genders are incomplete :(

gender is the only one incomplete, and bd might be not much reliable too
